Improved Description of Cation Binding to Lipid Bilayer with Negatively Charged POPS by Effective Inclusion of Electronic Polarization

### 2019-07-10 Manuscript/manuscript.tex
Updated Fig 3 "changes of OPs w.r.t. nacl and kcl" made a common legend, grouped together plots for PC and PS and placed ABCD to make it a nice panel

\begin{figure}[tbp!] 
  \centering 
  \includegraphics[height=\figheightsmall]{../img/ecc_pops/order_parameters_changes_ecc-lip_L14_A-B-PN-COO_POPC_kcl.pdf} 
  \includegraphics[height=\figheightsmall]{../img/ecc_pops/order_parameters_changes_ecc-lip_L14_A-B-PN-COO_POPC_nacl.pdf} 
  \includegraphics[height=\figheightsmall]{../img/ecc_pops/order_parameters_changes_ecc-lip_L14_A-B-PN-COO_POPS_kcl.pdf} 
  \includegraphics[height=\figheightsmall]{../img/ecc_pops/order_parameters_changes_ecc-lip_L14_A-B-PN-COO_POPS_nacl.pdf} 
  \caption{\label{fig:delta_ordPar_monoval_PCPS}
    Changes of the head group order parameters, and the angles of P--N and ${\rm{C}}_\beta-{\rm{C}}_\gamma$ (stars) vectors
    with respect to the membrane normal of POPC (left) and POPS (right) in a POPC:POPS (5:1) bilayer 
    as a function of \ce{KCl} and \ce{NaCl} concentration from ECC-lipids and Lipid17/Dang simulations 
    compared with experimental values from Ref. \citenum{roux90} (signs from Ref. \citenum{ferreira16}) at 298 K.
    The y-axis for the $\alpha$-carbon results of POPS (middle right) is transferred
    with the same value for both order parameters such that the lower order
    parameter value from pure POPS is at zero to correctly illustrate the significant forking.
    Because experimental data with \ce{NaCl} is not available for POPC, the data for KCl and \ce{LiCl} (dashed line, left)
    are shown as lower and upper bounds, respectively, for the response to \ce{NaCl}. Error bars are not visible for ECC-lipids simulations because they are smaller than the point size.}
\todo{J: Will improve this figure with panels A, B, C and D 
and put POPC together, POPS together 
and remove the duplicate y-axis titles 
and make a common legend distinguishing different experiments better. } \\
\todo{The scale in left and right columns (response to KCl and NaCl) should be the same (not necessarily the same scale for POPC and POPS though).}
\end{figure}

>>>>

\begin{figure}[tbp!] 
  \centering 
  %\includegraphics[height=\figheightsmall]{../img/ecc_pops/order_parameters_changes_ecc-lip_L14_A-B-PN-COO_POPC_kcl.pdf} 
  %\includegraphics[height=\figheightsmall]{../img/ecc_pops/order_parameters_changes_ecc-lip_L14_A-B-PN-COO_POPC_nacl.pdf} 
  %\includegraphics[height=\figheightsmall]{../img/ecc_pops/order_parameters_changes_ecc-lip_L14_A-B-PN-COO_POPS_kcl.pdf} 
  %\includegraphics[height=\figheightsmall]{../img/ecc_pops/order_parameters_changes_ecc-lip_L14_A-B-PN-COO_POPS_nacl.pdf} 
  \includegraphics[width=\figwidthfull]{../img/deltaOP_nacl_kcl_PC-PS.pdf} 
  \caption{\label{fig:delta_ordPar_monoval_PCPS}
    Changes of the head group order parameters, and the angles of P--N and ${\rm{C}}_\beta-{\rm{C}}_\gamma$ (stars) vectors
    with respect to the membrane normal of POPC (A, B) and POPS (C, D) in a POPC:POPS (5:1) bilayer 
    as a function of \ce{KCl} and \ce{NaCl} concentration from ECC-lipids and Lipid17/Dang simulations 
    compared with experimental values from Ref. \citenum{roux90} (signs from Ref. \citenum{ferreira16}) at 298 K.
    The y-axis for the $\alpha$-carbon results of POPS (middle right) is transferred
    with the same value for both order parameters such that the lower order
    parameter value from pure POPS is at zero to correctly illustrate the significant forking.
    Because experimental data with \ce{NaCl} is not available for POPC, the data for KCl and \ce{LiCl} (dashed line, left)
    are shown as lower and upper bounds, respectively, for the response to \ce{NaCl}. 
    Error bars are not visible for ECC-lipids simulations because they are smaller than the point size.}
\end{figure}
